Current Models

### 2018-03-19 models.Rmd
update the model script and description

AutoArima (Automatic Auto-Regressive Integrated Moving Average) is a 
flexible Auto-Regressive Integrated Moving Average (ARIMA) model fit to the 
data at the composite (full site and just control plots) spatial level
and the composite (community) ecological level. The model is selected and 
fitted using the `auto.arima` (with the `lambda` argument set to 0) and 
`forecast` functions in the **forecast** package [@Hyndman2013; @Hyndman2017]
and the `forecast_autoarima` function in our **portalPredictions** package 
[@PortalPredictions].

>>>>

AutoArima (Automatic Auto-Regressive Integrated Moving Average) is a 
flexible Auto-Regressive Integrated Moving Average (ARIMA) model fit to the 
data at the composite (full site and just control plots) spatial level
and the composite (community) ecological level. The model is selected and 
fitted using the `auto.arima` and `forecast` functions in the **forecast**
package [@Hyndman2013; @Hyndman2017] and the `forecast_autoarima` function 
in our **portalPredictions** package [@PortalPredictions].
